
\subsubsection{Preface}

\subsubsection{Introduction}

\subsubsection{Company Background} 
    \begin{itemize}
        \item Who/what are Nissens? (recently boosted with finincial capital), Development
        \item what does nissens offer? 
        \item How are the market Nissen are competing at working? (High Bargaining Power) (orders winner, orders qualifier)
            \item What/who are Nissens competitors and customers?
            \item what is Nissan's revenue stream? (Core competence, order winner, focus)
        \item strategy (5 must win battles, order fulfillment)
    \end{itemize}

\subsubsection{Problematization}
    \begin{itemize}
        \item Problem from Market
        \item Problem from Theory
        \item Problem from Nissen
    \end{itemize}

Initial Problem Statement: 

\subsubsection{Initial Analysis}
    \begin{itemize}
        \item (1) Mapping Services
        \item (2) Relationship between services and...
            \begin{itemize}
                \item Volume analysis: Relationship between quantity ( number of orders) of services? 
                \item Customers (are there a correlation between certain customers ordering certain service?)
                \item Products (are certain services bundled with certain products?)
                \item Service - commonality (similarities, differences?)
                \item Cost, profitability?
                \item Procedure/process variation? (customization-standardization degree)
                %\item Customization degree
                %\item Age
                %\item Departments/people
                %\item Volume/variety chart
            \end{itemize}
        \item (3) Consequences of offering these service (effect and cost)
            \item Control Elements in Nissens Services system: are they present? What is the effect of (not) having these in place?
    \end{itemize}

\subsubsection{Problem Statement}

\subsubsection{Analysis/solution work}

\subsubsection{Discussion}

\subsubsection{Conclusion}

\subsubsection{Reflections}

